---
title: "rs-ws-03-1"
author: "santowsa, CoWeber, aschupp"
date: "19 November 2017"
output: html_document
---

## White areas
Please identify the reason for the white boarders and sketch a potential solution which will remove the boarders but preserves the general geometry of the aerial images tiles of 2 by 2 km.

1. Identify overlaying raster data and read it in with stack function

```{r, echo=FALSE}
library(raster)
library(sp)
library(rgdal)

r3=stack("F:/rs/aerial_croped/raster3_crop.tif")
r4=stack("F:/rs/aerial_croped/raster4_crop.tif")
r5=stack("F:/rs/aerial_croped/raster5_crop.tif")            
r6=stack("F:/rs/aerial_croped/raster6_crop.tif")
```
2. Application of the overlay function, check right projection and save raster as new data for raster 3 and 4 

```{r, echo=FALSE}
r3_4 <- overlay(r3, r4, fun=min)

projection(r3_4) <- CRS("+init=epsg:25832")

writeRaster(r3_4, "F:/rs/aerial_croped/r3_4_new", format="GTiff")
```
3. Application of the overlay function, check right projection and save raster as new data for raster 5 and 6 

```{r,echo=FALSE}
r5_6 <- overlay(r5, r6, fun=min)

projection(r5_6) <- CRS("+init=epsg:25832")

writeRaster(r5_6, "F:/rs/aerial_croped/r5_6_new", format="GTiff")
```
