---
title: "rs-ws-06-1"
author: "CoWeber, aschupp, santowsa"
date: "5 Januar 2018"
output: html_document
---

# Land-cover classification [random forest]
## Under application of R, QGis and OTB

### 1. Create a raster stack of RGB and calculated filters as the basis of the random forest classification 

```{r, eval =FALSE}
library(raster)
setwd("D:/mpg/daten/areal/aerial_croped/caldern_ges")

r1 <- stack("merge_caldern.tif")
r2 <- raster("NGRDI_mean_9x9_caldern.tif")
r3 <- raster("NGRDI_variance_9x9_caldern.tif")

raster_rf <- stack(r1, r2, r3)
projection(raster_rf) <- CRS("+init=epsg:25832")
#summary(raster_rf)
writeRaster(raster_rf, "raster_rf", format = "GTiff")
```

### 2. Implementation of land use classification using QGIS and OSGeo4W-Shell

2.1 Train Image Classifier [OTB]:
Using only the Caldern RGB and the revised shp.-file
```{r, eval=FALSE}
otbcli_TrainImagesClassifier -io.il "C:\Users\Admin\Desktop\training_cal\merge_caldern.tif" -io.vd "C:\Users\Admin\Desktop\training_cal\merge_cal_shp.shp"  
-sample.mv 100 -sample.mt 100 -sample.vtr 0.5 -sample.vfn LN_new -classifier rf -io.out "C:\Users\Admin\Desktop\training_cal\model_11.txt" -io.confmatout "C:\Users\Admin\Desktop\training_cal\matrix_11.xml"
```

We also test the training with a new raster created in 1. and get the following error:

```{r, eval=FALSE}
C:\>otbcli_TrainImagesClassifier -io.il "D:\mpg\daten\areal\aerial_croped\calder
n_ges\raster_rf.tif" -io.vd "D:\mpg\daten\ln\merge_cal_shp.shp"  -sample.mv 100
-sample.mt 100 -sample.vtr 0.5 -sample.vfn LN_new -classifier rf -io.out "D:\mpg
\daten\ln\model_1.txt" -io.confmatout "D:\mpg\daten\ln\matrix_1.xml"

2018 Jan 05 17:22:28  :  Application.logger  (DEBUG) Entering DoExecute
2018 Jan 05 17:22:29  :  Application.logger  (INFO) Elevation management: settin
g default height above ellipsoid to 0 meters
2018 Jan 05 17:31:33  :  Application.logger  (INFO) Number of training samples:
3853
2018 Jan 05 17:31:33  :  Application.logger  (INFO) Size of training set: 3853
2018 Jan 05 17:31:33  :  Application.logger  (INFO) Size of validation set: 3779

2018 Jan 05 17:31:33  :  Application.logger  (INFO) Size of labeled training set
: 3853
2018 Jan 05 17:31:33  :  Application.logger  (INFO) Size of labeled validation s
et: 3779
OpenCV Error: Bad argument (1827-th value of 3-th (ordered) variable (=-1.#INF)
is too large) in CvDTreeTrainData::set_data, file C:\OSGeo4W64\usr\src\osgeo4w\o
pencv\opencv-2.4.11\modules\ml\src\tree.cpp, line 551
2018 Jan 05 17:31:33  :  Application.logger  (FATAL) The following error occurre
d during application execution : C:\OSGeo4W64\usr\src\osgeo4w\opencv\opencv-2.4.
11\modules\ml\src\tree.cpp:551: error: (-5) 1827-th value of 3-th (ordered) vari
able (=-1.#INF) is too large in function CvDTreeTrainData::set_data
```


2.2 Image Classifier [OTB]:

```{r, eval=FALSE}
otbcli_ImageClassifier -in "C:/Users/Admin/Desktop/training_cal/merge_caldern.tif" -model C:/Users/Admin/Desktop/training_cal/model_11.txt -ram 128 -out "C:\Users\Admin\Desktop\training_cal\classified_test.tif"
```


### 3. Land-cover classification of caldern univerity forest and environs


```{r, echo=FALSE} 
library(raster)
ras <- raster("D:/mpg/daten/areal/aerial_croped/caldern_ges/rf_class_1.tif")
plot(ras, col= terrain.colors(50), main = "Land-cover classification")
```

Relating to the classification results the differentiation between fields and meadows is sub-optimal. Also the classes of water, forest and meadows are overlap each other in different regions. 

According to our impression we think it's necessary to increase the baseline dataset with more informations, like different filters. The training areas should be fine in the meantime. 
