---
title: "Untitled"
author: "aschupp, cweber, santowsa"
date: "12 November 2017"
output: html_document
---
# W03-1

###Bitte "wd" bzw. den Dateipfad entsprechend der Datei hessen_holzeinschlag_1997-2014_clean.csv setzten.

#### 1. Please write an R script which reads the file, "isolates" the tabulated information and writes this information back to a new file called "hessen_holzeinschlag_1997-2014_clean.csv".
```{r}
df=read.csv("F:/Master/da-ws-03/W03/hessen_holzeinschlag_1997-2014.csv", skip=4, header=T, sep=";", dec=".")
df=df[-19,]
write.table(df,"F:/Master/da-ws-03/W03/hessen_holzeinschlag_1997-2014_clean.csv", dec=",", sep=";")
```
#W03-2

```{r}
df1=read.csv("F:/Master/da-ws-03/W03/hessen_holzeinschlag_1997-2014_clean.csv", header=T, sep=";", dec=",")
```
#### 1. Create a simple visualization which gives a quick, temporally non explicit and descriptive statistical overview of the harvest by tree type and as a total over all trees. 
```{r}
summary(df1)
bo=boxplot(df1[,2:7], main="Holzeinschlag 1997-2014",xlab="Baumart", ylab="Einschlagsmenge")
```

#### 2. Have a look at beech and spruce and write exactly one sentence for each of the tree species which summarizes what you see.

Beech: Smaller variation range and a equeal distribution between the quartiles.

Spruce: Higher variation range with an uneven distribution between the quartiles and a single outlier above the normal data range.


#### 3. Create another visualization which - in the same figure panel - shows how each beech harvest over the time span is related to each of the oak, pine, spruce and colored wood harvests in a 2 by 2 grid.
```{r}
a=cbind(df1$Buche,df1$Fichte)
b=cbind(df1$Buche,df1$Eiche)
c=cbind(df1$Buche,df1$Buntholz)
d=cbind(df1$Buche,df1$Kiefer)
e=df1$FWJ
matplot(e,a, pch=16, main="Buche und Fichte", xlab = "Jahr", ylab = "Einschlagsmenge", xaxt="n")
  legend("right", c("Buche","Fichte"), pch=16, col=c("black","red"),cex=0.6)
  axis(1, at=c(1997:2014))
matplot(e,b, pch = 16, main="Buche und Eiche", xlab = "Jahr", ylab = "Einschlagsmenge", xaxt="n")
  legend("right", c("Buche","Eiche"), pch=16, col = c("black", "red"), cex = 0.6)
  axis(1, at=c(1997:2014))
matplot(e,c, pch = 16, main="Buche und Buntholz", xlab = "Jahr", ylab = "Einschlagsmenge", xaxt="n")
  legend("right", c("Buche","Buntholz"), pch=16, col = c("black", "red"), cex = 0.6)
  axis(1, at=c(1997:2014))
matplot(e,d, pch = 16, main="Buche und Kiefer", xlab = "Jahr", ylab = "Einschlagsmenge", xaxt="n")
  legend("right", c("Buche","Kiefer"), pch=16, col = c("black", "red"), cex = 0.6)
  axis(1, at=c(1997:2014))
```

#### 4. Describe each plot with exactly one sentence.

The differnce between beech and spruce harvest is marginal, the outliner (2007) from spruce and a few higher spruce harvests (2002-2010) are visible.

Oak harvest is far below the beech harvest while similar trends are visible in both harvests.

Since the coloured wood data is NA since 2000 you can't compare this data.

Pine harvest has a continual growth with some episodal declines while beech harvest is consistent with a decline in the years 2006-2009.