---
title: "gi-ws-04-1"
author: "aschupp, CoWeber, santowsa"
date: "4 Dezember 2017"
output: html_document
---

#gi-ws-04-1

###A proper "for sequence" for selecting the raster window (total raster size) will follow.
###Also a proper and 'easy' own written function will come after the tutorial held by Jannis tomorrow.
```{r, eval=FALSE}
mainDir="F:/gIs/Projekte/pointcloud_processing"
inDir="/input/alldata/"
outDir="/output/alldata/"
Fusion="F:/gIs/FUSION/"

library(sp)
library(raster)
library(rgdal)

#creating a overview for the size of the dataframe (raster)

las_files<-list.files(paste0(mainDir,inDir), pattern=".las$", 
                      full.names=TRUE,recursive = TRUE) 

lapply(las_files, write,paste0(mainDir,inDir,"lidar_files.txt"), append=T)

system(paste0(Fusion, "catalog.exe ",mainDir, inDir, "lidar_files.txt " ,
              mainDir, outDir, "info_caldern.html"))

#creating the canopycover of the choosen rastersize

system(paste0(Fusion, "clipdata.exe", " /height /dtm:",mainDir, outDir,
              "caldern_GridSurf.dtm ", mainDir, inDir, "lidar_files.txt ", 
              mainDir, outDir, "caldern_normalized_point_cloud_LIDAR.las ", 
              "474000 5630000 479000 5634000"))

system(paste0(Fusion, "clipdata.exe"," /zpercent:95 ",  mainDir, outDir, 
              "caldern_normalized_point_cloud_LIDAR.las ", mainDir, outDir, 
              "caldern_normalized_point_cloud_LIDAR_zper_95.las ", 
              "474000 5630000 479000 5634000")) 

system(paste0(Fusion, "returndensity.exe ",mainDir,outDir, 
              "point_count_all_point_cloud_LIDAR_zper_95.dtm ", "1 ", 
              mainDir, outDir, "caldern_normalized_point_cloud_LIDAR_zper_95.las"))

system(paste0(Fusion, "dtm2ascii.exe ",mainDir,outDir, 
              "point_count_all_point_cloud_LIDAR_zper_95.dtm ", 
              mainDir,outDir, 
              "point_count_all_point_cloud_LIDAR_zper_95.asc"))

a=raster(file.path(mainDir,outDir,"point_count_all_point_cloud_LIDAR_zper_95.asc"))
writeRaster(a, paste0(mainDir,outDir,"caldern_canopy_cov"),format="GTiff")

#creating the 'all return' raster 

system(paste0(Fusion, "clipdata.exe", " /height /dtm:",mainDir, outDir,
              "caldern_GridSurf.dtm ", mainDir, inDir, "lidar_files.txt ", 
              mainDir, outDir, "caldern_normalized_point_cloud_LIDAR.las ", 
              "474000 5630000 479000 5634000"))

system(paste0(Fusion, "returndensity.exe ",mainDir,outDir, 
              "caldern_normalized_point_cloud_LIDAR.dtm ", "1 ", 
              mainDir, outDir, "caldern_normalized_point_cloud_LIDAR.las"))

system(paste0(Fusion, "dtm2ascii.exe ",mainDir,outDir, 
              "caldern_normalized_point_cloud_LIDAR.dtm ", 
              mainDir,outDir, 
              "caldern_normalized_point_cloud_LIDAR.asc"))

c=raster(file.path(mainDir,outDir,"caldern_normalized_point_cloud_LIDAR.asc"))
writeRaster(c, paste0(mainDir,outDir,"all_ret_cal"),format="GTiff")

#dividing canopy cover from all returns

a=raster(paste0(mainDir,outDir,"caldern_canopy_cov.tif"))
b=raster(paste0(mainDir,outDir, "all_ret_cal.tif"))
c=a/b
writeRaster(c, paste0(mainDir,outDir,"cp_div_all_cal"),format="GTiff")
```


```{r,echo=TRUE}
mainDir="F:/gIs/Projekte/pointcloud_processing"
inDir="/input/alldata/"
outDir="/output/alldata/"
Fusion="F:/gIs/FUSION/"

library(sp)
library(raster)
library(rgdal)
d=raster(paste0(mainDir,outDir, "cp_div_all_cal.tif"))
plot(d)
```

As you can see we took somewhere the wrong exit and got stuck with a wrong display of CP/all returns.

As stated above we will search for the error and replace it with the correct data string.