---
title: "W02-1 Loop and conquer"
author: "Alexander Santowski"
date: "5 November 2017"
output: html_document
---

#Group: aschupp, santowsa, CoWeber

1: Implement a if-then-else statement which prints "Larger" if the number provided as variable ''n'' is larger than 1 and "Equal or smaller" oterhwise.

```{r}
n=readline(prompt="Wählen Sie eine ganze Zahl aus: ")
n=as.numeric(n)
#Test n=1.
n=1
if (n>1) print('Larger') else print('Equal or Smaller')
```


2: Extent a copy of the above statement which returns "Equal" and "Smaller" explicitly in addition to "Larger".

```{r}
n=readline(prompt="Wählen Sie eine ganze Zahl aus: ")
n=as.numeric(n)
#Test n=1.
n=1
if (n>1) print('Larger') else if (n==1) print('Equal') else print('Smaller')
```


3: Implement a if-then-else statement which prints "Even" if the number provided as variable ''n'' is even and which prints "Odd" otherwise.

```{r}
n=readline(prompt="Wählen Sie eine ganze Zahl aus: ")
n=as.numeric(n)
#Test n=1.
n=1
if (n%%2==0) print('Even') else print('Odd')
```


4: Copy task 2 and include it into a 'for loop' which shows that all three options are actually implemented in a correct manner by iterating over n from a number which is smaller 1, exactly 1 and larger than 1.

```{r}
for (n in seq(0,2)) if (n>1) print('Larger') else if (n==1) print('Equal') else print('Smaller')
```


5: Extent a copy of the above loop and modify the loop and if-then-else statement in such a way, that the information on "Larger" etc. is not printed on the screen but saved within a vector (i.e. a variable which will hold all three statements in the end). Print the content of this vector after the loop.

```{r}
c=c()
for (n in seq(0,2)) if (n>1) c[n+1]=('Larger') else if (n==1) c[n+1]=('Equal') else c[n+1]=('Smaller')
print(c)
```


6: Extent a copy of #5 in such a way, that the results are not saved in a vector but a list. Print the content of this list after the loop.

```{r}
c=list()
for (n in seq(0,2)) if (n>1) c[n+1]=('Larger') else if (n==1) c[n+1]=('Equal') else c[n+1]=('Smaller')
print(c)
```


7: Change the above modified loop in such a way, that the iteration is controlled by a lapply not a for loop. Save the returning information from the lapply function in a variable and print the content of this variable after the loop.

```{r}
results=lapply(seq (0,2), function(n){if (n>1) c[n+1]=('Larger') else if (n==1) c[n+1]=('Equal') else c[n+1]=('Smaller')})
print(results)
```


8: Finally change the above variable in such a way that the content is not printed as a nested list but a vector.

```{r}
results=lapply(seq (0,2), function(n){if (n>1) c[n+1]=('Larger') else if (n==1) c[n+1]=('Equal') else c[n+1]=('Smaller')})
results=unlist(results)
print(results)
```
