---
title: "Untitled"
author: "aschupp, cweber, santowsa"
date: "12 November 2017"
output: html_document
---
#W03-1
Please write an R script which reads the file, "isolates" the tabulated information and writes this information back to a new file called "hessen_holzeinschlag_1997-2014_clean.csv".
```{r}
df=read.csv("F:/Data_analysis/data/hessen_holzeinschlag_1997-2014.csv", skip=4, header=T, sep=";", dec=",")
df=df[-19,]
write.table(df, "F:/Data_analysis/data/hessen_holzeinschlag_1997-2014_clean.csv", dec=",", sep=";")
```
#W03-2
Bitte "wd" entsprechend der Datei hessen_holzeinschlag_1997-2014_clean.csv setzten.
```{r}
df1=read.csv("F:/Data_analysis/data/hessen_holzeinschlag_1997-2014_clean.csv", header=T, sep=";", dec=",")
```
Create a simple visualization which gives a quick, temporally non explicit and descriptive statistical overview of the harvest by tree type and as a total over all trees. 
```{r}
summary(df1)
bo=boxplot(df1[,2:7], main="Holzeinschlag 1997-2014",xlab="Baumart", ylab="Einschlagsmenge")
```
Have a look at beech and spruce and write exactly one sentence for each of the tree species which summarizes what you see.


Create another visualization which - in the same figure panel - shows how each beech harvest over the time span is related to each of the oak, pine, spruce and colored wood harvests in a 2 by 2 grid.
```{r}
a=cbind(df1$Buche,df1$Fichte)
b=cbind(df1$Buche,df1$Eiche)
c=cbind(df1$Buche,df1$Buntholz)
d=cbind(df1$Buche,df1$Kiefer)
e=df1$FWJ
matplot(e,a, pch=16, main="Buche und Fichte", xlab = "Jahr", ylab = "Einschlagsmenge", xaxt="n")
  legend("right", c("Buche","Fichte"), pch=16, col=c("black","red"),cex=0.6)
  axis(1, at=c(1997:2014))
matplot(e,b, pch = 16, main="Buche und Eiche", xlab = "Jahr", ylab = "Einschlagsmenge", xaxt="n")
  legend("right", c("Buche","Eiche"), pch=16, col = c("black", "red"), cex = 0.6)
  axis(1, at=c(1997:2014))
matplot(e,c, pch = 16, main="Buche und Buntholz", xlab = "Jahr", ylab = "Einschlagsmenge", xaxt="n")
  legend("right", c("Buche","Buntholz"), pch=16, col = c("black", "red"), cex = 0.6)
  axis(1, at=c(1997:2014))
matplot(e,d, pch = 16, main="Buche und Kiefer", xlab = "Jahr", ylab = "Einschlagsmenge", xaxt="n")
  legend("right", c("Buche","Kiefer"), pch=16, col = c("black", "red"), cex = 0.6)
  axis(1, at=c(1997:2014))
```
Describe each plot with exactly one sentence.
