---
title: "da-ws-10-1"
author: "CoWeber, aschupp, santowsa"
date: "28 Januar 2018"
output: html_document
---

# Precipitation forecast (DWD station Coelbe)

### Workflow for precipiation forecast

- (1) Data preparation
- (2) Calculate ARIMA model with different parameter combination
- (3) Best model by RMSE and auto-arima
- (4) Plot results 


## (1) Data preparation
```{r}
#install.packages("forecast")
library(forecast)
mainDir <- "D:/mpg/daten/dwd_coelbe/"
results <- "results"
### read dwd data:
dwd <- read.table(paste0(mainDir,"produkt_synop_Terminwerte_20060701_20151231_03164.txt"),
                  header = T, sep = ";")
#head(dwd)
### create new colum with year and month info from MESS_DATUM:
dwd$AGG_M <- substr(dwd$MESS_DATUM, 1, 6)
#head(dwd$AGG_M)
### aggregate the monthly precipitation:
df <- aggregate(dwd$NIEDERSCHLAGSHOEHE, by=list(dwd$AGG_M), FUN= sum)
colnames(df) <- c("Date", "NSH") #new colnames
head(df)

### Splitting data into train (07/2006-12/2013) and test (01/2014-12/2015)
time <- which(df$Date == 201312)
train <- df[1:time,] 
test <- df[(time+1):(nrow(df)),] 

### parameter combination for ARIMA: 

para <- expand.grid(p=seq(0,5), d=seq(0,2), q=seq(0,5),
                   ps=seq(0,2), ds=seq(0,2), qs=seq(0,2))
#(para)
```

## (2) Calculate ARIMA model with different parameter combination

```{r, warning=FALSE}
### ARIMA model with all parameters:
result <- lapply(seq(nrow(para)), function(x){
  mod <- arima(train$NSH, 
               order = c(para$p[x], para$d[x], para$q[x]),
               seasonal = list(order = c(para$ps[x], para$ds[x], para$qs[x])),
               method = "ML")
  pre <- predict(mod, n.ahead = 24)
  
  return(data.frame(p = para$p[x], d = para$d[x], q = para$q[x],
                    ps = para$ps[x], ds = para$ds[x], qs = para$qs[x],
                    rmse = sqrt(mean((pre$pred - test$NSH)^2))))
})

### save the ARIMA-results:

saveRDS(result, file = paste0(mainDir, "arima_nsh_model.RDS"))
``` 

## (3) Best model by RMSE and auto-arima

```{r}

### get results just for .RMD output
result <- readRDS(paste0(mainDir,"arima_nsh_model.RDS"))
result <- do.call("rbind", result)

### best model with smallest rmse:
best <- result[min(result$rmse),]
### get the model with the best parameters:
best_model <- arima(train$NSH,
                  order = c(best$p,best$d,best$q),
                  seasonal = list(order = c(best$ps, best$ds, best$qs)),
                  method = "ML")
best_pred <- predict(best_model, n.ahead = 24)

### using auto arima function for comparison optimal model and corresponding values:
ts_prec <- ts(train$NSH, start = c(2006, 7), end = c(2013, 12), frequency = 12)
auto_mod <- forecast::auto.arima(ts_prec, max.p = 5, max.d = 2, max.q = 5, 
                                 stationary = TRUE, seasonal = TRUE)

### calculate statistics for best mode:
best$AIC <- best_model$aic
stats <- data.frame(p = 2, d = 0, q = 2, ps = NA, ds = NA, qs = NA, 
                         rmse = summary(auto_mod)[2], AIC = auto_mod$aic)

### print summarized statistics:
mod_stats <- rbind(best, stats)
rownames(mod_stats) <- c("ARIMA", "auto_ARIMA")
print(mod_stats)
```

## (4) Plot results

```{r}
prec_ts <- ts(df$NSH, start = c(2006, 7), end = c(2015, 12), frequency = 12)
pred_ts <- ts(best_pred$pred, start = c(2014, 1), end = c(2015, 12), frequency = 12)
pred_se <- ts(best_pred$se, start = c(2014, 1), end = c(2015, 12), frequency = 12)
plot(prec_ts, main = "Arima (3,1,1)(0,0,0)", ylab = "NSH", xlab="Years")
lines(pred_ts, col="green")
lines(pred_ts+pred_se, col ="blue")
lines(pred_ts-pred_se, col ="blue")
legend("topleft",legend=c("Forecast Arima 3,1,1", "Forcast Arima 0,0,0"), col = c("green","blue"), 
        lty= 1:1, cex=0.8)
```

```{r}
plot(forecast(auto_mod), main = "Auto Arima (2,0,2)", ylab = "NSH", xlab="Years")
lines(prec_ts, col="black", lty= 2)
legend("topleft", legend=c("NHS-values", "Auto Arima"), col = c("black", "blue"), lty=2:1, cex=0.8)
```

### One-sentence-statement about differences:

- There are no significant differences at RMSE and AIC of the two models even if the plot shows a better adapted auto-ARIMA model. 
